Sweep A - general experiment analysis.

### 2019-05-21 voltagebudget/analysis/exp106_analysis.Rmd
WIP

```{r, message=FALSE}
exp <- "106"
g_ls <- c("10e-9", "12e-9", "14e-9")

@@

# As

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*mV, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc*mV, y=n_spikes_pop - n_spikes_ref, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=g_l)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

>>>>

```{r, message=FALSE}
exp <- "106"
g_ls <- c("10e-9", "12e-9", "14e-9", "16e-9")

@@

# As
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*mV, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# Variance
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc * mV, y=variances_pop*ms, color=g_l)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  group_by(g_l) %>% 
  mutate(variances_pop=normalize(variances_pop)) %>% 
  mutate(errors_pop=normalize(errors_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances_pop, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

# Error
```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop*ms, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  group_by(g_l) %>% 
  mutate(variances_pop=normalize(variances_pop)) %>% 
  mutate(errors_pop=normalize(errors_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors_pop, color=g_l)) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

# Ratio ests
```{r, fig.width=1}
ratios <- NULL
for (V in c("10e-9", "12e-9", "14e-9")) {
  tmp <- filter(results, g_l == V, N == 1, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, as.numeric(V))
  ratios <- rbind(ratios, row)
}
ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
colnames(ratios) <- c("error_50", "ratio", "g_l")
# Get ratio

ratios %>% 
  ggplot(aes(x=g_l*1e9, ratio)) + 
  geom_point() + 
  theme_classic()
```

# Trade off
```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms, color=g_l)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(N == 1, V_osc/V_comp < 5) %>% 
  group_by(g_l) %>% 
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, y=errors_pop, color=g_l)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

### 2019-05-21 voltagebudget/analysis/exp107_analysis.Rmd
WIP

# Ratio ests
```{r}
ratios <- NULL
for (V in c("-70e-3", "-72e-3", "-74e-3", "-76e-3")){
  tmp <- filter(results, V_l == V, N == 1, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, as.numeric(V))
  ratios <- rbind(ratios, row)
}
ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
colnames(ratios) <- c("error_50", "ratio", "V_l")
# Get ratio

ratios %>% 
  ggplot(aes(x=V_l, ratio)) + 
  geom_point() + 
  theme_classic()
```

>>>>

# Ratio ests
```{r, fig.width=1}
ratios <- NULL
for (V in c("-70e-3", "-72e-3", "-74e-3", "-76e-3")){
  tmp <- filter(results, V_l == V, N == 1, V_osc/V_comp < 5)
  pnts <- find_point(normalize(tmp$errors_pop), tmp$V_osc/tmp$V_comp, 0.5)  
  row <- c(pnts, as.numeric(V))
  ratios <- rbind(ratios, row)
}
ratios <- as.data.frame(ratios, stringsAsFactors=FALSE)
colnames(ratios) <- c("error_50", "ratio", "V_l")
# Get ratio

ratios %>% 
  ggplot(aes(x=V_l*mV, ratio)) + 
  geom_point() + 
  theme_classic()
```
